Estimating Comparative Advantage in Improved Seed Adoption: Hybrid Maize in Ethiopia

### 2021-11-24 paper.tex

Table \ref{tbl:summary} shows a set of summary statistics for our sample. The mean parcel size for a household is about 0.15 Ha, with a maximum size of a little less than 1.5 Ha. Harvest labor is disproportionately skewed to family participation with around 20 days of harvest labor being conducted by family members and only about 2 days for hired labor. This

@@

@@

Methods

>>>>

Table \ref{tbl:summary} shows a set of summary statistics for our sample. The mean parcel size for a household is about 0.15 Ha, with a maximum size of a little less than 1.5 Ha. Harvest labor is disproportionately skewed to family participation with around 20 days of harvest labor being conducted by family members and only about 2 days for hired labor. This is indicative of either malfunctioning labor markets, income constraints or high supervision costs. The distances to some key areas are also highlighted in Table \ref{tbl:summary}. On average households are around 13 kilometers away from an asphalt road and almost 60 kilometers away from the nearest market. This makes both the purchase of improved seed and the marketing of yields subject to transportation costs and a difficult enterprise. Fertilizer costs are on average 8,350 Birr (~178 USD) and with a large amount of the sample not using fertilizer at all. This is particularly important in the context of improved maize seed use as it requires fertilizer to be most effective. Only 5\% of the sample irrigates their crops making households susceptible weather shocks.

@@

The ESS has has both self-reported

@@
